
## 1.2  Install packages and load libraries
```{r, include=FALSE, cache=TRUE, message = FALSE}
library(sp)
library(sf)
library(tmap)
library(tmaptools)
library(sf)
library(geojsonio)
library(dplyr)
library(ggplot2)
library(ggthemes)
```

```{r, eval = FALSE}
library(sp)
library(sf)
library(tmap)
library(tmaptools)
library(sf)
library(geojsonio)
library(dplyr)
library(ggplot2)
library(ggthemes)
```

```{r, results="hide",cache=TRUE, message = FALSE}
# Get the London LSOA Boundaries
LD_MSOA <- st_read(
  'D:/F_SCUA-UCL/CASA05/workshop_1/statistical-gis-boundaries-london/statistical-gis-boundaries-london/ESRI/MSOA_2011_London_gen_MHW.shp')   #You can change it to your own path
```

The next step is to calculate the area of each region for further analysis
```{r, cache=TRUE, message = FALSE}
# Calculate area
LD_MSOA_area <- st_area(LD_MSOA)
LD_MSOA_area <- LD_MSOA_area %>% as.numeric(as.character(LD_MSOA_area))

# Add a colomn of area to LD_LSOA
LD_MSOA$area<- LD_MSOA_area

# Transform geographic coordinate to 4326
LD_MSOA <-  LD_MSOA %>%
  st_transform(4326)

# Remove useless data 
LD_MSOA <- LD_MSOA %>%
  select('MSOA11CD', 'MSOA11NM','POPDEN', 'geometry', 'area')
head(LD_MSOA)
```


## 2.1 Neighborhood living
### 2.3.1 Road network density

```{r, cache=TRUE, message = FALSE}
# Read data
LD_road <- st_read('D:/F_SCUA-UCL/Final/GIS_Final/data/street/gis_osm_roads_free_1.shp')

# Intersect the road and boundaries
road_intersect <- LD_road %>%
  st_join(., LD_MSOA)

# Calculate the length of road in each region
length <- st_length(road_intersect)
length <- as.numeric(length)
road_intersect$length <- length


# Calculate the account length of each region
road_intersect <- road_intersect %>%
  group_by(MSOA11CD, ) %>%
  summarise(.,sum(length))

# Remove NA
road_intersect <- road_intersect%>%
  filter(MSOA11CD != '')%>%
  st_drop_geometry()

# Join the road data to LD_LSOA
MSOA_road_account <- left_join(LD_MSOA, road_intersect, by=c('MSOA11CD'= 'MSOA11CD'))

# Calculate road density
MSOA_road_account$density <- MSOA_road_account$`sum(length)` / MSOA_road_account$area
```

```{r, cache=TRUE, message = FALSE}
# plot
tm_shape(MSOA_road_account)+
  ## boundries
  tm_borders(col = "white",alpha = 0.01, lwd = 0.01)+
  ## fill color
  tm_fill(col = 'density',n = 5,style = 'quantile', palette = "Blues",colorNA = "gray",
          legend.show = TRUE,legend.hist = FALSE,
          title = 'Road Density',text.size = 0.1)+
  tm_compass(size = 2.5, text.size = 0.7, type = "arrow", position=c("left", "bottom"))+ #compass
  tm_scale_bar(width = 0.15, position=c("left", "bottom"), text.size = 0.5)+   ## bar
  # tm_xlab("Longitude") + tm_ylab("Latitude")  # coordinate
  tm_layout(title = "c.Small Block", 
            main.title = "", title.size = 1)
```

### 2.3.2 POIs density and diversity
POI data is the data for September 2019 and downloaded from the digimap (<https://digimap.edina.ac.uk/>, Ordnance Survey > Data Download > Boundary and Location Data). which providing a full range of topographic Ordnance Survey data. There are 353532 points in Greater London. 

1） Process data of POI
```{r,cache=TRUE, message = FALSE}

# Read data
poi <- st_read('D:/F_SCUA-UCL/Final/GIS_Final/data/POI/POI.shp')
## Data Copyright Note
## Ordnance Survey Digimap: Licensed Data: © Crown copyright and database rights 2020 Ordnance Survey (100025252). 
## This material includes data licensed from PointX© Database Right/Copyright 2020.

# Remove useless data 
poi_LD <- poi %>%
  select('ref_no', 'name','groupname', 'geographic', 'categoryna', 'classname', 'geometry')

# PLOT Points heat map to view the data
poi_LD <- poi_LD %>%
  st_transform(4326) %>% # tranform to same CRS as stations and lines
  cbind(st_coordinates(.))
### Add boundaries of borough (LSOA is too small)
Londonborough <- st_read(
  'D:/F_SCUA-UCL/CASA05/workshop_1/statistical-gis-boundaries-london/statistical-gis-boundaries-london/ESRI/London_Borough_Excluding_MHW.shp')

### plot heatmap
```
Clean data 
```{r message=FALSE}

# Remove points outside of London
poi_LD_clean <- poi_LD %>%
  filter(geographic == 'Greater London')
poi_MSOA <- poi_LD_clean %>%
  st_join(., LD_MSOA)

```

Step1 Divide the total number of POIs by the area to get the result of POIs density.
```{r, cache=TRUE, message = FALSE}

# count points of each LOSA
poi_count <- poi_MSOA %>%
  group_by(MSOA11CD) %>%
  summarise(n=n())
poi_count <- poi_count %>% 
  st_drop_geometry()

# add the numbers of points to LOSA (then can calculate density and plot)
MSOA_POI_account <- left_join(LD_MSOA, poi_count, by=c('MSOA11CD'= 'MSOA11CD'))
MSOA_POI_account$density <- MSOA_POI_account$n / MSOA_POI_account$area

```

Plot **POI density**
```{r, cache=TRUE, message = FALSE}

tm_shape(MSOA_POI_account)+
  tm_borders(col = "white",alpha = 0.01, lwd = 0.01)+
  tm_fill(col = 'density',n = 5,style = 'quantile', palette = "YlGnBu",colorNA = "gray",
          legend.show = TRUE,legend.hist = FALSE,
          title = 'MSOA_POI_account')+
  tm_compass(size = 2.5, text.size = 0.7, type = "arrow", position=c("left", "bottom"))+ #compass
  tm_scale_bar(width = 0.15, position=c("left", "bottom"), text.size = 0.5)+   ## bar
  tm_layout(title = "a.Mixed-use", 
            main.title = "", title.size = 0.77) 
```

Step2 Count all types of POI to get the result of POIs diversity. 
```{r,cache=TRUE, message = FALSE}
# Create a 'Richness' metric by 'Group', "Category' and 'Class'
div_tab <- poi_MSOA %>%
  st_drop_geometry() %>%
  group_by(MSOA11CD) %>%
  summarise(rich_g = n_distinct(groupname),
            rich_cat = n_distinct(categoryna),
            rich_cla = n_distinct(classname))

# Merge
diversity <- MSOA_POI_account %>%
  merge(., div_tab)

diversity$rich_cla_den <- diversity$rich_cla / diversity$area
```
Plot **POI density**
```{r, cache=TRUE, message = FALSE}
## plot
tm_shape(diversity)+
  ## boundries
  tm_borders(col = "white",alpha = 0.01, lwd = 0.01)+
  ## fill color
  tm_fill(col = 'rich_cla_den',n = 5,style = 'quantile', palette = "YlGnBu",colorNA = "gray",
          legend.show = TRUE,legend.hist = FALSE,
          title = 'POI_Diversity')+
  tm_compass(size = 2.5, text.size = 0.7, type = "arrow", position=c("left", "bottom"))+ #compass
  tm_scale_bar(width = 0.15, position=c("left", "bottom"), text.size = 0.5)+   ## bar
  # tm_xlab("Longitude") + tm_ylab("Latitude")  # coordinate
  tm_layout(title = "c.Diversity of Points of Interest(per m2)", 
            main.title = "", title.size = 0.77) 
```


### 2.3.3 the building age
plot **the building age**. 
```{r, cache=TRUE, message = FALSE}
building_age <- read.csv('D:/F_SCUA-UCL/Final of year/FINAL/1.csv')

head(building_age)

building_age <- building_age %>%
  filter(GEOGRAPHY == 'MSOA' )

building_age$mean <- ( building_age$BP_PRE_1900 * 0 + building_age$BP_1900_1918 * 9 + building_age$BP_1919_1929 * 24 +
  building_age$BP_1930_1939 * 35 + building_age$BP_1945_1954 * 50 + building_age$BP_1955_1964 * 60 + building_age$BP_1965_1972 *69 + 
  building_age$BP_1973_1982 * 78 + building_age$BP_1983_1992 * 88 + building_age$BP_1993_1999 * 96 + building_age$BP_2000_2009 * 105 +
  building_age$BP_2010_2015 * 103 ) / (building_age$BP_PRE_1900 + building_age$BP_1900_1918 + building_age$BP_1919_1929 +
                                       building_age$BP_1930_1939 + building_age$BP_1945_1954 + building_age$BP_1955_1964 + building_age$BP_1965_1972 + 
                                       building_age$BP_1973_1982 + building_age$BP_1983_1992 + building_age$BP_1993_1999 + building_age$BP_2000_2009 +
                                       building_age$BP_2010_2015+ 0.00000001)

BA <- building_age %>%
  group_by(ECODE)%>%
  summarise(.,mean(mean))

BA <- BA %>%
  rename(., bamean = 'mean(mean)')

MSOA_road_account <- left_join(MSOA_road_account, BA, by = c('MSOA11CD' = 'ECODE'))
# plot
tm_shape(MSOA_road_account)+
  ## boundries
  tm_borders(col = "white",alpha = 0.01, lwd = 0.01)+
  ## fill color
  tm_fill(col = 'bamean',n = 5,style = 'quantile', palette = "YlGnBu",colorNA = "gray",
          legend.show = TRUE,legend.hist = FALSE,
          title = 'Road Density')+
  tm_compass(size = 2.5, text.size = 0.7, type = "arrow", position=c("left", "bottom"))+ #compass
  tm_scale_bar(width = 0.15, position=c("left", "bottom"), text.size = 0.5)+   ## bar
  # tm_xlab("Longitude") + tm_ylab("Latitude")  # coordinate
  tm_layout(title = "d. Population Density", 
            main.title = "", title.size = 0.77) 
```

# 3. Data Cleaning and Distribution Visualization

## 3.2 Distribution Visualization
```{r,cache=TRUE, message = FALSE}
# Select POI_density
Independentdata <- select(MSOA_POI_account, MSOA11CD, density) %>%
  rename(.,POI_density = density)
# Select POI_diversity
POI_diversity <- select(diversity,MSOA11CD,rich_cla_den) %>%
  st_drop_geometry()
Independentdata <- left_join(Independentdata, POI_diversity, by=c('MSOA11CD'= 'MSOA11CD'))
Independentdata <- rename(Independentdata,POI_diversity = rich_cla_den)
# Select Road_density
Road_density <- select(MSOA_road_account,MSOA11CD,density,bamean) %>%
  st_drop_geometry()
Independentdata <- left_join(Independentdata, Road_density, by=c('MSOA11CD'= 'MSOA11CD'))
Independentdata <-rename(Independentdata, Road_density = density)
# drop geo inf
Independentdata <- Independentdata %>%
  st_drop_geometry()
```


```{r}
fourindex <- Independentdata 
fourindex <- left_join(fourindex, LD_MSOA, by=c('MSOA11CD'='MSOA11CD'))
fourindex <- select(fourindex,-MSOA11NM, -area)

#POI density
minPd <- min(fourindex$POI_density)
Pd <- max(fourindex$POI_density) - min(fourindex$POI_density)
pd_norm <-  fourindex$POI_density - minPd
fourindex$pd_norm <- pd_norm / Pd

#POI diversity
minPdiv <- min(fourindex$POI_diversity)
Pdiv <- max(fourindex$POI_diversity) - min(fourindex$POI_diversity)
pdiv_norm <-  fourindex$POI_diversity - minPdiv
fourindex$pdiv_norm <- pdiv_norm / Pdiv

#Road density
minR <- min(fourindex$Road_density)
R <- max(fourindex$Road_density) - min(fourindex$Road_density)
r_norm <- fourindex$Road_density - minR
fourindex$r_norm <- r_norm / R

#Population density
minPpla <- min(fourindex$POPDEN)
Ppla <- max(fourindex$POPDEN) - min(fourindex$POPDEN)
Ppla_norm <- fourindex$POPDEN - minPpla
fourindex$Ppla_norm <- Ppla_norm / Ppla

#ba density
minPp <- min(fourindex$bamean)
Pp <- max(fourindex$bamean) - min(fourindex$bamean)
Pp_norm <- fourindex$bamean - minPp
fourindex$Pp_norm <- Pp_norm / Pp

four_index <- fourindex %>%
  select(.,MSOA11CD, pd_norm,pdiv_norm ,Ppla_norm,Pp_norm,r_norm)

four_index$mixed <- four_index$pd_norm * 0.5 + four_index$pdiv_norm * 0.5
four_index$ba_norm <- 1 - four_index$Pp_norm 
```

```{r}
four_index_GEO <- left_join( LD_MSOA,four_index, by = c('MSOA11CD' = 'MSOA11CD')) %>%
  select(.,-MSOA11NM,-area)

# mixed
tm_shape(four_index_GEO)+
  ## boundries
  tm_borders(col = "white",alpha = 0.01, lwd = 0.01)+
  ## fill color
  tm_fill(col = 'mixed',n = 5,style = 'quantile', palette = "Blues",colorNA = "gray",
          legend.show = TRUE,legend.hist = FALSE,
          title = 'POI density&diversity')+
  tm_compass(size = 2.5, text.size = 0.7, type = "arrow", position=c("left", "bottom"))+ #compass
  tm_scale_bar(width = 0.15, position=c("left", "bottom"), text.size = 0.5)+   ## bar
  # tm_xlab("Longitude") + tm_ylab("Latitude")  # coordinate
  tm_layout(title = "a. Mixed_use", 
            main.title = "", title.size = 1) 

# old buildings
tm_shape(four_index_GEO)+
  ## boundries
  tm_borders(col = "white",alpha = 0.01, lwd = 0.01)+
  ## fill color
  tm_fill(col = 'Pp_norm',n = 5,style = 'quantile', palette = "Blues",colorNA = "gray",
          legend.show = TRUE,legend.hist = FALSE,
          title = 'age of buildings')+
  tm_compass(size = 2.5, text.size = 0.7, type = "arrow", position=c("left", "bottom"))+ #compass
  tm_scale_bar(width = 0.15, position=c("left", "bottom"), text.size = 0.5)+   ## bar
  # tm_xlab("Longitude") + tm_ylab("Latitude")  # coordinate
  tm_layout(title = "b. Old buildings", 
            main.title = "", title.size = 1) 

# block
tm_shape(four_index_GEO)+
  ## boundries
  tm_borders(col = "white",alpha = 0.01, lwd = 0.01)+
  ## fill color
  tm_fill(col = 'r_norm',n = 5,style = 'quantile', palette = "Blues",colorNA = "gray",
          legend.show = TRUE,legend.hist = FALSE,
          title = 'Road Density')+
  tm_compass(size = 2.5, text.size = 0.7, type = "arrow", position=c("left", "bottom"))+ #compass
  tm_scale_bar(width = 0.15, position=c("left", "bottom"), text.size = 0.5)+   ## bar
  # tm_xlab("Longitude") + tm_ylab("Latitude")  # coordinate
  tm_layout(title = "c. Small block", 
            main.title = "", title.size = 1) 

# old buildings
tm_shape(four_index_GEO)+
  ## boundries
  tm_borders(col = "white",alpha = 0.01, lwd = 0.01)+
  ## fill color
  tm_fill(col = 'POPDEN',n = 5,style = 'quantile', palette = "Blues",colorNA = "gray",
          legend.show = TRUE,legend.hist = FALSE,
          title = 'Density')+
  tm_compass(size = 2.5, text.size = 0.7, type = "arrow", position=c("left", "bottom"))+ #compass
  tm_scale_bar(width = 0.15, position=c("left", "bottom"), text.size = 0.5)+   ## bar
  # tm_xlab("Longitude") + tm_ylab("Latitude")  # coordinate
  tm_layout(title = "d. Density", 
            main.title = "", title.size = 1) 

```

```{r}
par(mfrow=c(1, 4))  # divide graph area in 2 columns
# The original data
boxplot(four_index$mixed, main="Mixed_use", col = '#b0c7f0')
boxplot(four_index$ba_norm, main="Building_age", col = '#b0c7f0')
boxplot(four_index$r_norm, main="small_block", col = '#b0c7f0')
boxplot(four_index$Ppla_norm, main="Density",col = '#b0c7f0')

```

None of them are Normal distribution so we make them to logarithmic
```{r, cache=TRUE, message = FALSE}
#log
four_index$log_mix <- log(four_index$mixed)
four_index$log_r <- log(four_index$r_norm)
four_index$log_pop <- log(four_index$Ppla_norm)
four_index$log_bamean <- log(four_index$ba_norm)

```

Show the data in boxlot
```{r, cache=TRUE, message = FALSE}

```


```{r, cache=TRUE, message = FALSE}
boxplot(Independentdata$bamean, main="Building_age", col = '#b0c7f0')
boxplot(Independentdata$log_POI_density, main="log_POI_density",col = '#b0c7f0')
boxplot(Independentdata$log_POI_diversity, main="log_POI_diversity", col = '#b0c7f0')
boxplot(Independentdata$log_Road_density, main="log_Road_density", col = '#b0c7f0')
boxplot(Independentdata$log_bamean, main="log_building_age",col = '#b0c7f0')
```

Show the data distribution in histgram
```{r, cache=TRUE, message = FALSE}
par(mfrow=c(2, 4))  # divide graph area in 2 columns
# The original data

hist(four_index$mixed, main="POI_density", col = '#b0c7f0')
hist(four_index$r_norm, main="POI_diversity",col = '#b0c7f0')
hist(four_index$Ppla_norm, main="Road_density", col = '#b0c7f0')
hist(four_index$ba_norm, main="Building_age", col = '#b0c7f0')

hist(four_index$log_mix, main="log_POI_density",col = '#b0c7f0')
hist(four_index$log_r, main="log_POI_diversity", col = '#b0c7f0')
hist(four_index$log_pop, main="log_Road_density", col = '#b0c7f0')
hist(four_index$log_bamean , main="log_Road_density", col = '#b0c7f0')



write.csv(four_index,file = 'fourindex.csv')
```


```{r, cache=TRUE, message = FALSE}
hist(Independentdata$log_bamean, main="log_Poplation_density",col = '#b0c7f0')
```

# 4. Neighborbood living index calculating
The calculation of the index uses the same weight to calculate the four indicators. unity-based normalization is used to bring all values into the range [0,1]. After the four indicators are normalized into same rage, the average is calculated to obtain the index. The normalization formula is:
**x'=  (x- x_min)/(x_max  - x_min )**

```{r, cache=TRUE, message = FALSE}
four_index_GEO$index <- four_index_GEO$mixed + four_index_GEO$r_norm + four_index_GEO$ba_norm + four_index_GEO$Ppla_norm
```

```{r}
tm_shape(four_index_GEO)+
  ## boundries
  tm_borders(col = "white",alpha = 0.01, lwd = 0.01)+
  ## fill color
  tm_fill(col = 'index',n = 5,style = 'quantile', palette = "Blues",colorNA = "gray",
          legend.show = TRUE,legend.hist = FALSE,
          title = 'Density')+
  tm_compass(size = 2.5, text.size = 0.7, type = "arrow", position=c("left", "bottom"))+ #compass
  tm_scale_bar(width = 0.15, position=c("left", "bottom"), text.size = 0.5)+   ## bar
  # tm_xlab("Longitude") + tm_ylab("Latitude")  # coordinate
  tm_layout(title = "Diversity", 
            main.title = "", title.size = 1) 
```

```{r}

```


```{r, cache=TRUE, message = FALSE}
flow <- read.csv() 
```

Determine whether the normal distribution by histogram

```{r, cache=TRUE, message = FALSE}
flow <- read.csv('D:/F_SCUA-UCL/Final of yeaer/Urban vitality/visual.csv') 

flow$sumod <- flow$o_flow + flow$d_flow

flow_data <- flow %>%
  select(., -MSOA11NM,-POPDEN,-X,-diff, -o_density, -d_density)

# view the data (whether it is normalize)
par(mfrow=c(1, 2),pin = c(3,2.5)) 
boxplot(flow_data$sumod, main="Flow")
hist(flow_data$sumod, main="Flow")

flow_dist <- flow_data %>%
  ggplot(aes(x=sumod)) +
  geom_histogram(position="identity", 
                 alpha=0.5, 
                 bins=15, 
                 fill="#b0c7f0", col="black")+
  geom_vline(aes(xintercept=mean(sumod)),
             color="darkblue",
             linetype="dashed")+
  labs(title="Neighborbood living index",
       x="log_index",
       y="Frequency")+
  theme_classic()+
  theme(plot.title = element_text(hjust = 0.5))
flow_dist
```
```{r}
flow_data$logsumod <- log(flow_data$sumod)

boxplot(flow_data$logsumod, main="Diversity",col = 'orange')

Dist <- flow_data %>%
  ggplot(aes(x=logsumod)) +
  geom_histogram(position="identity", 
                 alpha=0.5, 
                 bins=15, 
                 fill="red", col="black")+
  geom_vline(aes(xintercept=mean(logsumod)),
             color="darkblue",
             linetype="dashed")+
  labs(title="log of Flow",
       x="log of Flow",
       y="Frequency")+
  theme_classic()+
  theme(plot.title = element_text(hjust = 0.5))

Dist
```




```{r}

spatial_data <- four_index_GEO %>%
  select(.,MSOA11CD,mixed,ba_norm,r_norm,Ppla_norm,index)



qm_data <- left_join(spatial_data,flow_data,by=c('MSOA11CD' = 'MSOA11CD'))
ldnogep <- LD_MSOA %>%
  st_drop_geometry()
qm_data <- left_join(qm_data, ldnogep,by=c('MSOA11CD' = 'MSOA11CD')) 

qm_data$flowden <- qm_data$sumod /qm_data$POPDEN
qm_data$flowden <- qm_data$flowden /qm_data$area
```

```{r}

```


```{r}
# Select variables
corre_variable <- qm_data %>%
  select(.,-MSOA11CD)%>%
  st_drop_geometry()
# Plot it
library(corrplot)
cormat <- cor(corre_variable, use="complete.obs", method="pearson")
corrplot(cormat)

library(Hmisc)
res2 <- corre_variable 
res2 <- dplyr::mutate_all(res2,as.integer)
res <- rcorr(as.matrix(res2))
res
```


```{r}
relation <- lm(qm_data$sumod~qm_data$index)
print(summary(relation))
```


```{r}
relation <- lm(qm_data$d_flow~qm_data$index)

print(summary(relation))
```
```{r}
# Select data
Cluster_data <- corre_variable %>%
  select(sumod, index)

# translate data into int.
Cluster_data <- dplyr::mutate_all(Cluster_data,as.integer)

fit <- Cluster_data %>%
  kmeans(., 5, nstart=50)

# get cluster means

library(tidymodels)

centroid <- tidy(fit)%>%
  #print the results of the cluster groupings
  print()%>%
  dplyr::select(sumod,index)


```



```{r}
# Plot the clusters on a graph
p <- ggplot(Cluster_data,aes(flowden, index))+
  geom_point(aes(colour=factor(fit$cluster)))+
  geom_point(data=centroid,aes(denpoplog, index), size=7, shape=18)+ theme(legend.position="none")

clustering <- fit %>% 
  # 
  augment(., qm_data)%>%
  dplyr::select(MSOA11CD, .cluster)%>%
  #make sure the .cluster column is numeric
  mutate(across(.cluster, as.numeric))%>%
  # join the .cluster to our sf layer
  left_join(qm_data, 
            .,
            by = c("MSOA11CD" = "MSOA11CD"))



## make the scatter plot
qm_data$cluster <- clustering$.cluster
cluster_scatter <- ggplot(qm_data, aes(x=index,y=sumod,color = cluster))+
  geom_point(aes(colour = cluster))
cluster_scatter
```

```{r}

flow_cluster02 <- qm_data %>%
  filter(cluster ==4)%>%
  st_drop_geometry()
flow_cluster02$logflowden <- log(flow_cluster02$flowden)

```

```{r}
coremain <- flow_cluster02 %>%
  select(.,-cluster,-logmix,-logmixed)
corre_variable <- coremain %>%
  select(.,-MSOA11CD,-MSOA11NM, -POPDEN, -area, -sumod,-flowden, -mixed,-mix2)
# Plot it
library(corrplot)
cormat <- cor(corre_variable, use="complete.obs", method="pearson")
corrplot(cormat)

library(Hmisc)
res2 <- corre_variable 
res2 <- dplyr::mutate_all(res2,as.integer)
res <- rcorr(as.matrix(res2))
res
```

```{r}
relation <- lm(coremain$sumod~coremain$index)

print(summary(relation))

```

```{r}
relation <- lm(coremain$d_flow~coremain$index)

print(summary(relation))
```
```{r}
coremain11 <- flow_cluster01 %>%
  select(.,-cluster)
corre_variable <- coremain11 %>%
  select(.,-MSOA11CD)%>%
  st_drop_geometry()
# Plot it
library(corrplot)
cormat <- cor(corre_variable, use="complete.obs", method="pearson")
corrplot(cormat)

library(Hmisc)
res2 <- corre_variable 
res2 <- dplyr::mutate_all(res2,as.integer)
res <- rcorr(as.matrix(res2))
res
```


```{r}
# Select data
Cluster_data <- flow_cluster02 %>%
  select(index,sumod)%>%
  st_drop_geometry()

# translate data into int.
Cluster_data <- dplyr::mutate_all(Cluster_data,as.integer)

fit <- Cluster_data %>%
  kmeans(., 5, nstart=50)

# get cluster means

library(tidymodels)

centroid <- tidy(fit)%>%
  #print the results of the cluster groupings
  print()%>%
  dplyr::select(index,sumod)

```

```{r}
# Plot the clusters on a graph
p <- ggplot(Cluster_data,aes(index,sumod))+
  geom_point(aes(colour=factor(fit$cluster)))+
  geom_point(data=centroid,aes(index,sumodw), size=7, shape=18)+ theme(legend.position="none")

clustering <- fit %>% 
  # 
  augment(., flow_cluster02)%>%
  dplyr::select(MSOA11CD, .cluster)%>%
  #make sure the .cluster column is numeric
  mutate(across(.cluster, as.numeric))%>%
  # join the .cluster to our sf layer
  left_join(flow_cluster02, 
            .,
            by = c("MSOA11CD" = "MSOA11CD"))



## make the scatter plot
flow_cluster02$cluster <- clustering$.cluster
cluster_scatter <- ggplot(flow_cluster02, aes(x=index,y=sumod,color = cluster))+
  geom_point(aes(colour = cluster))
cluster_scatter

head(flow_cluster02)

scatter <- flow_cluster02 %>%
  filter(cluster != 4)%>%
  filter(cluster != 1)
```



```{r}
write.csv(qm_data, file='qm_data.csv')
write.csv(flow_cluster03, file='cluster01.csv')
write.csv(flow_cluster01, file='cluster02.csv')
write.csv(flow_cluster02, file='cluster03.csv')

```

```{r}
ggplot(scatter, aes(x=sumod,y=index),colour = sex)+geom_point()+ geom_smooth(method = lm)

scatter1 <- scatter %>%
  st_drop_geometry()
write.csv(scatter1, file='relationflowdiver.csv')


fit<-lm(logsumod~index,data=scatter1)  
summary(fit)  
```
```{r}
difference <- qm_data %>%
  select(MSOA11CD)
difference$inflow <- qm_data$d_flow - qm_data$o_flow
IN_OUT <- difference %>%
  filter(inflow >=0)
OUT_IN <- difference %>%
  filter(inflow <0) 
```

